---
title: "Lab11"
author: "Yi Wang"
date: "11/21/2018"
output: html_document
---

```{r}

```
#1. Write a function that generates numbers from binomial(n, p) distribution using runif() function. Hint: binomial(n, p) random variable can be defined as a sum of n independent Bernoulli(p) random variables.

```{r}

f <- function(s, n, p){
  rbi <- vector(length = s)
  for (i in 1: s) {
    rn <- runif(n)
    rb <- as.numeric(rn < p)
    rbi[i] <- sum(rb)
  }
    return(rbi)
}

```

#2. Compare performance of your function with rbinom() using microbenchmark() function.

```{r}
library(microbenchmark)
rbinom(100, 3, 0.5)
f(100, 3, 0.5)

microbenchmark(rbinom(100, 3, 0.5), f(100, 3, 0.5))
```

3. Suppose we want to simulate data from a linear regression model:

Yi = $\beta_0$ + $\beta_1$ × Xi + $\epsilon_i$ = 1, ..., N

where $\epsilon$ ~ N(0, 3) and X is a covariate that ranges between 20 and 40. Let $\beta_0$ = 15 and $\beta_1$ = 0.4 are known coefficients. Generate data (N = 50) from this models with given coefficients. Fit a linear regression model and plot fitted values vs residuals using ggplot() function. Please do not forget to use set.seed() function for reproducibility.

```{r}
library(ggplot2)
set.seed(123)
beta0 <- 15
beta1 <- 0.4
xl <- 20
xh <- 40
N <- 50
eps <- rnorm(N, 0, 3)
x <- runif(N, xl, xh)
y <- beta0 + beta1 * x + eps

fit <- lm(y~x)
fit

ggplot(mapping = aes(fit$fitted.values, fit$residuals)) +
  geom_point() + 
  labs(x = "Fitted value", y = "Risiduals", title = "Linear Regression Model")

```

4. Box-Muller algorithm: generate U1 and U2 two independent uniform(0, 1) random variables and set:
R = $\sqrt{−2log(U1)}$ and $\theta$ = 2$\pi$U2
then
X = Rcos($\theta$) and Y = Rsin($\theta$)
are two independent normal variables. Write a function that generates normal variates using Box-Muller algorithm. Compare simulated data from your function with simulated data from rnorm() function using ggplot() (histogram?).

```{r}
n = 5000;
U1 = runif(n)
U2 = runif(n)
X = sqrt(-2 * log(U1)) * cos(2 * pi * U2)
Y = sqrt(-2 * log(U1)) * sin(2 * pi * U2)
X1 <- rnorm(5000)

par(mfrow = c(1, 2))
ggplot() +
  geom_histogram(aes(Y), bins = 30, fill = "sky Blue") +
  geom_histogram(aes(X), bins = 30, col = "dark green", fill = NA) +
  geom_freqpoly(aes(X1), bins = 30, col = "red") +
  labs(x = "Simulated Data and rnorm") +
  theme_classic()

```

